noam_data_exploration_v1

### 2024-07-03 noam_data_exploration_v3.Rmd
Added "dplyr::" before summarise so code works consistently

---
title: "noam_data_exploration_v1"
author: "Noam Altman-Kurosaki"
date: "2024-05-09"
output: html_document
---

@@

transect_level <- long_data %>%
  dplyr::group_by(Year, Site, Habitat, Transect, Taxa) %>%
  summarise(Mean_cover = mean(Percent_cover), 
            SE = sd(Percent_cover)/sqrt(n()))

site_level <- transect_level %>%
  dplyr::group_by(Year, Site, Habitat, Taxa) %>%
  summarise(Mean_site_cover = mean(Mean_cover), 
            Site_se = sd(Mean_cover)/sqrt(n()))
```

@@

wide_transect_level <- data %>%
  dplyr::group_by(Year, Site, Habitat, Site_habitat, Transect) %>%
  summarize(across(all_of(species_cols), mean, na.rm = TRUE))

@@

alpha_diversity_means <- alpha_diversity %>%
  dplyr::group_by(Year, Site, Habitat, Site_habitat) %>%
  summarise(Richness_mean = mean(Richness), 
            Richness_se = sd(Richness)/sqrt(n()),
            Shannon_mean = mean(Shannon), 
            Shannon_se = sd(Shannon)/sqrt(n()))

@@

beta_disper_means <- stratum_distances %>%
  dplyr::group_by(Year, Site, Habitat, Site_habitat) %>%
  summarise(Distance_mean = mean(Distance), 
            Distance_se = sd(Distance)/sqrt(n()))

@@

diversity_stability <- alpha_diversity %>%
  dplyr::group_by(Site, Habitat, Site_habitat, Transect) %>%
  summarise(Richness_mean = mean(Richness), 
            Richness_se = sd(Richness)/sqrt(n()),
            Richness_cv = CV(Richness),
            Shannon_mean = mean(Shannon), 
            Shannon_se = sd(Shannon)/sqrt(n()),
            Shannon_cv = CV(Shannon),
            Cover_mean = mean(Cover),
            Cover_se = sd(Cover)/sqrt(n()),
            Cover_cv = CV(Cover))

@@

turnover_means <-
  total_turnover %>%
  dplyr::group_by(Year, Site, Habitat, Site_habitat) %>%
  summarise(Turnover_mean = mean(total), 
            Turnover_se = sd(total)/sqrt(n()))

@@

appearance_means <-
  appearance %>%
  dplyr::group_by(Year, Site, Habitat, Site_habitat) %>%
  summarise(Appearance_mean = mean(appearance), 
            Appearance_se = sd(appearance)/sqrt(n()))

@@

disappearance_means <-
  disappearance %>%
  dplyr::group_by(Year, Site, Habitat, Site_habitat) %>%
  summarise(Disappearance_mean = mean(disappearance), 
            Disappearance_se = sd(disappearance)/sqrt(n()))

@@

rank_shift_means <-
  rank_shift %>%
  dplyr::group_by(Year, Site, Habitat, Site_habitat) %>%
  summarise(Rank_shift_mean = mean(MRS), 
            Rank_shift_se = sd(MRS)/sqrt(n()))

>>>>

---
title: "noam_data_exploration_v1"
author: "Noam Altman-Kurosaki"
date: "2024-05-09"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

transect_level <- long_data %>%
  dplyr::group_by(Year, Site, Habitat, Transect, Taxa) %>%
  dplyr::summarise(Mean_cover = mean(Percent_cover), 
            SE = sd(Percent_cover)/sqrt(n()))

site_level <- transect_level %>%
  dplyr::group_by(Year, Site, Habitat, Taxa) %>%
  dplyr::summarise(Mean_site_cover = mean(Mean_cover), 
            Site_se = sd(Mean_cover)/sqrt(n()))
```

@@

wide_transect_level <- data %>%
  dplyr::group_by(Year, Site, Habitat, Site_habitat, Transect) %>%
  dplyr::summarize(across(all_of(species_cols), mean, na.rm = TRUE))

@@

alpha_diversity_means <- alpha_diversity %>%
  dplyr::group_by(Year, Site, Habitat, Site_habitat) %>%
  dplyr::summarise(Richness_mean = mean(Richness), 
            Richness_se = sd(Richness)/sqrt(n()),
            Shannon_mean = mean(Shannon), 
            Shannon_se = sd(Shannon)/sqrt(n()))

@@

beta_disper_means <- stratum_distances %>%
  dplyr::group_by(Year, Site, Habitat, Site_habitat) %>%
  dplyr::summarise(Distance_mean = mean(Distance), 
            Distance_se = sd(Distance)/sqrt(n()))

@@

diversity_stability <- alpha_diversity %>%
  dplyr::group_by(Site, Habitat, Site_habitat, Transect) %>%
  dplyr::summarise(Richness_mean = mean(Richness), 
            Richness_se = sd(Richness)/sqrt(n()),
            Richness_cv = CV(Richness),
            Shannon_mean = mean(Shannon), 
            Shannon_se = sd(Shannon)/sqrt(n()),
            Shannon_cv = CV(Shannon),
            Cover_mean = mean(Cover),
            Cover_se = sd(Cover)/sqrt(n()),
            Cover_cv = CV(Cover))

@@

turnover_means <-
  total_turnover %>%
  dplyr::group_by(Year, Site, Habitat, Site_habitat) %>%
  dplyr::summarise(Turnover_mean = mean(total), 
            Turnover_se = sd(total)/sqrt(n()))

@@

appearance_means <-
  appearance %>%
  dplyr::group_by(Year, Site, Habitat, Site_habitat) %>%
  dplyr::summarise(Appearance_mean = mean(appearance), 
            Appearance_se = sd(appearance)/sqrt(n()))

@@

disappearance_means <-
  disappearance %>%
  dplyr::group_by(Year, Site, Habitat, Site_habitat) %>%
  dplyr::summarise(Disappearance_mean = mean(disappearance), 
            Disappearance_se = sd(disappearance)/sqrt(n()))

@@

rank_shift_means <-
  rank_shift %>%
  dplyr::group_by(Year, Site, Habitat, Site_habitat) %>%
  dplyr::summarise(Rank_shift_mean = mean(MRS), 
            Rank_shift_se = sd(MRS)/sqrt(n()))
